Identifying regime transitions for water governance at a basin scale

### 2022-04-28 paper/main/04_discussion.tex
fix(version,-abstract): new version 5.1.3, references updated, main text checked

\subsection{Challenges along with the transition}

@@

% Implications
Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being \cite{best2019, best2020}.
As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships \cite{diaz2019}.
The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime \cite{reyers2018}.

@@

%* limitations & direction
One of the main limitations in the approach is the few data worldwide with a long-term period, which means still a gap between the comprehensively identifying and widespread application of IWGI.
However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically.
In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
\cite{cumming2018,cumming2014,jaeger2019}.
Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
\cite{gleeson2020, wang-erlandsson2022}.
A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability
\cite{falkenmark2019}.

>>>>

@@

% Implications
Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being
\cite{best2019,best2020}.
As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships \cite{diaz2019}.
The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
It is vital for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily applicable under a different regime \cite{reyers2018}.

@@

%* limitations & direction
One of the main limitations in the approach is the few data worldwide with a long-term period, which means still a gap between the comprehensively identifying and widespread application of IWGI.
However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
Therefore, we suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically.
In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
\cite{cumming2018,cumming2014,jaeger2019}.
Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
\cite{gleeson2020, wang-erlandsson2022}.
A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability
\cite{falkenmark2019}.

### 2022-04-28 paper/main/manuscript.tex
fix(version,-abstract): new version 5.1.3, references updated, main text checked

\abstract{
    In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
    Identifying regime changes is critical to understanding the transition and guiding sustainability in water governance.
    We combined three main dimensions -stress, purpose and allocation- to develop a quantitative Integrated Water Governance Index (IWGI) to detect water governance regimes at a basin scale.
    Applying the IWGI to a rapidly-changing basin (the Yellow River Basin, China) describes how water governance shifts between the massive supply regime, governance transformation regime, and adaptation oriented regime.
    In the YRB, the regime shifts' underlying causes were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation.
    The IWGI offers a comprehensive and straightforward approach to linking the water governance regimes to the following challenges in sustainability, along with the hydrosocial transition.
}

>>>>

\abstract{
    In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how. Therefore, identifying regime changes is critical to understanding the transition and guiding sustainability in water governance. We combined three main dimensions -stress, purpose and allocation- to develop a quantitative Integrated Water Governance Index (IWGI) to detect water governance regimes at a basin scale. Applying the IWGI to a rapidly-changing basin (the Yellow River Basin, China) describes how water governance shifts between massive supply, transformation governance, and adaptation-oriented regimes. In the YRB, the regime shifts' underlying causes were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation. The IWGI offers a comprehensive and straightforward approach to linking the water governance regimes to the following challenges in sustainability, along with the hydrosocial transition.
}
